Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-02-28 paper/EDA.qmd
Added Install Packges for instruction when running the code. Use it via unmarking #hastage signs. Another note Added Graph for tesing Homogeneity of  Vaiance & Normality and made graph

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)
library(kableExtra)

@@

>>>>

# Make sure Packages are installed

# install.packages("tidyverse")
# install.packages("janitor")
# install.packages("here")
# install.packages("lubridate")
# install.packages("arrow")
# install.packages("dplyr")
# install.packages("knitr")
# install.packages("performance")
# install.packages("kableExtra")
# install.packages("performance")
```

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)
library(kableExtra)
library(performance)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Assumption Check for Time taken after taking the Drug"

# Fit ANOVA Model
model <- aov(game_after ~ drug, data = clean_data)

# Check Model Assumptions
check_model(model, check = c("normality", "homogeneity"))
```

```{r}
#| include: false
#| warning: false
#| message: false
# Barlett Test Homegenity of Variance: testing for ass
# bartlett_test <- bartlett.test(game_after ~ drug, data = clean_data)
# print(bartlett_test)
```
